\section{Objectives}
\subsection{Phase One (Fall 2013)}
\indent To produce FEMs of the simply supported beams which concur with analytical solutions and indicate the modal response. Design and produce a sensory package to collect accurate vibration data. Compare experimental data with FEM. \\
\subsection{Phase Two (Spring 2014)}
\indent To modify the sensory package design to be installed on the Pell Bridge by being power independent and wireless communication capabilities. Model the Pell Newport Bridge to predict modal frequency.\\
\section{Layout} %FIX ME!!!!!!!!!!!!!!!!
This report will discuss the planning process of designing a sensor package intended to evaluate vibration on the Pell Bridge. As this is a two-semester project the preliminary assembly of the package was simplified to evaluate vibrations of a 6.8 meter angle beam. A finite element model was produced of this angle beam to provide information on the modes of vibration and natural frequency. \\
\indent The extension of this project will include modifying the sensor package to be implemented on the Newport Bridge. A Finite Element Modeling will be drawn in Abaqus to indicate where we should install the sensors and what the natural frequency of the bridge will approximately be. \\
\indent Chapter 3 will explains the finite element model of the angle beam and what parameters were used to describe the material. To prove that the finite element model was reflecting accurate natural frequencies and modes of vibration, these model was verified with the analytical solution for the beam, this evaluation is described in detail in chapter 3. \\
\indent Choosing the appropriate, cooperating instrumentation is integral to producing a sensor package that will accurately monitor the bridge. Chapter 4 of this report will present the instrumentation chosen and why. \\
\indent After the preliminary package was assembled data was collected and processed for the 6.8 meter angle beam. The collection process and processing details are discussed in chapter 5 and 6. \\ 
\indent As this sensor package is intend for the Pell Newport Bridge necessary modifications were researched for remote installation. Power independence is required along with wireless communication capabilities. The intended modifications are discussed in chapter 7. 